\begin{enumerate}
    \item Code and comments must be written in English.
    \item Code must be written in C/C++.
    \item Every function must have a doxygen comment above.
    % doxygen rules
    \item Comments must be written above the code descripted.
    \item Pre-defined values must be defined using \lstinline{#define}.
    \item DEFINE macros must be written in capital letters.
    \item include guards must end with six random letters or numbers.
    \item naming
    \begin{enumerate}[label=\arabic*.]
        \item spaces are written as underscores \lstinline{_}.
        \item functions
        \begin{enumerate}[label=\arabic*.]
            \item First letter must be written in Capital.
        \end{enumerate}
        \item variables
        \begin{enumerate}[label=\arabic*.]
            \item Capital letters must not be used.
            \item \lstinline{int} variables must start with \lstinline{i_}
            \item \lstinline{long} variables must start with \lstinline{l_}
            \item \lstinline{long long} variables must start with \lstinline{ll_}
            \item \lstinline{uint8_t} variables must start with \lstinline{u8_}
            \item \lstinline{uint16_t} variables must start with \lstinline{u16_}
            \item \lstinline{uint32_t} variables must start with \lstinline{u32_}
            \item \lstinline{uint64_t} variables must start with \lstinline{u64_}
            \item \lstinline{bool} variables must start with \lstinline{bool_}
            \item \lstinline{float} variables must start with \lstinline{fl_}
            \item \lstinline{char} variables must start with \lstinline{ch_}
            \item strings must start with \lstinline{str_}
            \item vectors must start with \lstinline{vec_}
            \item \item \lstinline{enum} variables must start with \lstinline{en_}
            \item transfer parameters begin with an underscore \lstinline{_} in addition to the above.
            \item Variables of a \lstinline{typedef enum} start with the starting letters of the originating type listed above.
        \end{enumerate}
        \item classes
        \begin{enumerate}[label=\arabic*.]
            \item classes must start with \lstinline{cla_}
            \item objects created from a class must start with \lstinline{obj_}
        \end{enumerate}
    \end{enumerate}
    \item All variables in classes must be protected or private, if getter and setter methods don't exceed proportionate effort.
    % clang-format rules.
\end{enumerate}